An Authoritative Adventure

### 2019-12-27 article.tex
Added an "article" class and example to create small adventure document (unlike the book, no title page or table of contents)

\documentclass[letterpaper,twocolumn,openany]{dndbook}

@@

\usepackage[utf8]{inputenc}
\usepackage[singlelinecheck=false]{caption}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{shortvrb}
\usepackage{stfloats}

\captionsetup[table]{labelformat=empty,font={sf,sc,bf,},skip=0pt}

% Set the default background paper-like image. This options allows it to be overridden.
\paperimage{img/paper}

@@

\title{The Dark \LaTeX{} \\
\large An Example of the dndbook Class}
\author{The rpgTeX Team}
\date{2019/07/18}

@@

\frontmatter

@@

\tableofcontents

\mainmatter%

\chapter{Sections}

\DndDropCapLine{T}{his package is designed to aid you in} writing beautifully typeset documents for the fifth edition of the world's greatest roleplaying game. It starts by adjusting the section formatting from the defaults in \LaTeX{} to something a bit more familiar to the reader. The chapter formatting is displayed above.

@@

\chapter{Text Boxes}

@@

\section{As an Aside}
The other two environments are the |DndComment| and the |DndSidebar|. The |DndComment| is breakable and can safely be used inline in the text.

@@

\section{Tables}
The |DndTable| colors the even rows and is set to the width of a line by default.

@@

\chapter{Monsters and NPCs}

@@

\chapter{Colors}

@@

\section{Themed Colors}
Use |\DndSetThemeColor[<color>]| to set |commentcolor|, |readaloudcolor|, |sidebarcolor|, and |tablecolor| to a specific color. Calling |\DndSetThemeColor| without an argument sets those colors to the current |themecolor|. In the following example the group limits the change to just a few boxes; after the group finishes, the colors are reverted to what they were before the group started.

>>>>

\documentclass[letterpaper,twocolumn,openany]{dndarticle}

@@

\usepackage[utf8]{inputenc}
\usepackage[singlelinecheck=false]{caption}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{shortvrb}
\usepackage{stfloats}
\usepackage{graphicx}
\usepackage{titling}

\captionsetup[table]{labelformat=empty,font={sf,sc,bf,},skip=0pt}
\DndSetThemeColor[DmgLavender]

% Override the default background "paper" image with an alternate one.
\paperimage{img/paper-article}

@@

\font\quipfont=cmr7 at 8pt
\title{An Authoritative Adventure}
\author{@author}
\date{{\quipfont \small\textit{A short quip that describes the adventure, such as ``Who will survive the attack of the murder-hobos?''}}}

% Adds an article image at the top of column 1 above the title, similar to the
% "Dungeon"-style article. Comment out the below to remove the image.
\pretitle{
  \Huge
  \vspace{-30pt} % Align top of image with column 2.
  \centering{\includegraphics[width=7cm,height=7cm]{img/title.jpg}\\[\bigskipamount]}
  \begin{center}
}
\posttitle{\end{center}}

@@

@@

\DndDropCapLine{T}{his package is designed to aid you in} writing beautifully typeset documents for the fifth edition of the world's greatest roleplaying game. It starts by adjusting the section formatting from the defaults in \LaTeX{} to something a bit more familiar to the reader. The article formatting is displayed above.

The default title layout is reminiscent of the article format in publications such as Dungeon magazine.

@@

\section{Text Boxes}

@@

\subsection{As an Aside}
The other two environments are the |DndComment| and the |DndSidebar|. The |DndComment| is breakable and can safely be used inline in the text.

@@

\subsection{Tables}
The |DndTable| colors the even rows and is set to the width of a line by default.

@@

\section{Monsters and NPCs}

@@

\section{Colors}

@@

\subsection{Themed Colors}
Use |\DndSetThemeColor[<color>]| to set |commentcolor|, |readaloudcolor|, |sidebarcolor|, and |tablecolor| to a specific color. Calling |\DndSetThemeColor| without an argument sets those colors to the current |themecolor|. In the following example the group limits the change to just a few boxes; after the group finishes, the colors are reverted to what they were before the group started.
